cardinalR: Generating interesting high-dimensional data structures

### 2025-04-29 paper-cardinalR.Rmd
Updated
Added additional_functions.R

```{r}
interior_annotation <- function(label, position = c(0.92, 0.92), cex = 1, col="grey70") {
  annotation_custom(grid::textGrob(label = label,
                                   x = unit(position[1], "npc"), y = unit(position[2], "npc"),
                                   gp = grid::gpar(cex = cex, col=col)))
}
```

# Introduction

@@

>>>>

```{r}
#| label: import-scripts
source("scripts/additional_functions.R")
```
# Introduction

@@

The main arguments of the ```gen_multicluster()``` function are shown in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:main-tb-html)', '\\@ref(tab:main-tb-pdf)'))`.
